Windowed Developer Topic Analysis

### 2009-03-20 lda-paper.tex
More lda paper

\section{Results}
%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird

@@

@@

In this study we are explicitly trusting that the programmers annotate
their changes with relevant information. We rely on the descriptions
they provide. If the language of checkin comments was automated

We truncated the topics to top 10 tokens, this summary of a topic
might not have been as useful as determining the actual topic distance
between two word topic distributions.

>>>>

\section{Results}

We applied our tools and visualizations to the repositories of
multiple database systems.

%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird

@@

The plots we produced of MaxDB 7.500 were interesting, there was a
period where no real development occured and thus there were no topics
whatsoever. We have two periods to evaluate for MaxDB 7.500, the first
period from June 2004 to jan 2005, and the second period from June
2005 to June 2006.

The largest common trend has references to build system files like
SYSDD.punix and MONITOR.punix etc. Other tokens mentioned are Sutcheck
v1.09, the prefix SUT stands for Storable Unit Type. Sutcheck would
also automate perforce check-ins.

The second largest common trend seems to be a side effect of an
automated checkin which is annotated as ``implicit checkin''. These
were checkins that were produced when importing changes from an
external Perforce repository.

The third most common trend, seen on Figure \ref{fig:trend}, seemed to
include tokens related to operating system support, such as Linux and
Windows, as well as architecture support, AMD64 and Opteron. The word
problem was common among all of those trends. This trend seemed
related to the smaller fourth largest trend which occurred nearby it
that had AMD64 and Windows tokens.

@@

In this study we are explicitly trusting that the programmers annotate
their changes with relevant information. We rely on the descriptions
they provide. If the language of checkin comments was automated we
would only be analyzing that.

We truncated the topics to top 10 tokens, this summary of a topic
might not have been as useful as determining the actual topic distance
between two word topic distributions. By truncating tokens we could be
losing valuable data.

Each project seemed to have their own kind of stop words, we did not
remove them, but perhaps dropping some of these stop words would aid
the clarity of such topic clusters, alternatively it might cause our
topic similarity plots to be fundamentally different. Perhaps our
methods of suggesting that topics are similar is not appropriate.

The number of commits per month is inconsistent some months have a lot
of changes where as some months have almost none.
